Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-02-07 paper/paper.tex
editing the experimental section

% common experiment settings
Every experiment is replicated several times to take random effects into account, e.g.
random network initialization prior to training, randomly ordered batches during SGD.
Unless specified otherwise, every experiment uses global gradient clipping within an
$\ell_2$-norm ball of radius $0.5$, runs SGD with ADAM optimizer with the base learning
rate of $10^{-3}$ which is scaled after $5$, $10$, and $20$ epochs by $\tfrac1{10}$,
$\tfrac1{20}$ and $\tfrac1{100}$, respectively.

\subsection{Staged fitting and compression} % (fold)
\label{sub:fitting_and_compression}

The goal of this section to study the compression-performance trade-off of the proposed Bayesian
sparsification methods for $\cplx$-valued networks. To this end we employ the following training
plan in every experiment. The model is trained in three successive stages: ``dense'' $\to$
``sparsify'' $\to$ ``fine-tune''. Model parameters and the optimizer are copied between
stages, except before the ``fine-tune'' optimizer's internal state is reset.

At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
non-Bayesian architecture and using only the likelihood term from \eqref{eq:elbo} without
variational dropout.
%
During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes}) or its $\real$
counterpart. To be able to study the attainable sparsity levels we inject a coefficient $
  C \in (0, 1]
$ at the KL divergence term in \eqref{eq:elbo}:
\begin{equation}  \label{eq:elbo_with_coef}
    - \frac{C}N KL(q_{\theta} \| \pi_{\lambda})
    + \frac1{M} \sum_{i=1}^M
        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
    \,. \tag{\ref{eq:elbo}'}
\end{equation}
Higher $C$ yields increasingly more sparse layers upon termination of this stage.
%
The \textit{``fine-tune''} stage begins with computing the sparsity masks from the fitted
approximation $q_\theta(W)$ and proceeds to train the non-zero parameters similarly to
the ``dense'' stage, i.e. with non-Bayesian layers and fixed sparsity masks.

% on compresssion
Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
the variational approximation factorizes into univariate distributions, whether a $\cplx$
or $\real$ parameter is zero or not is determined from individual relevance scores $
  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff}
displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset
in sec.~\ref{sub:mnist_like_datasets}. This shape appears to be typical in every experiment
conducted in this study: there always is a single mode within the moderately negative
range, and one or two modes to the right of zero. The relative mass of each mode changes
with $C$ and the higher the coefficient is, the more mass is shifted to the right. In every
experiment the trough between the peaks of the negative mode and the first positive one
is around zero.

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__threshold.pdf}
  \end{subfigure}
  \caption{%
    Smoothed density of $\log\alpha$ for a convolutional and dense layer from a model
    in sec.~\ref{sub:mnist_like_datasets}.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

% on chosing the threshold
The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
are within $\delta$ relative tolerance of their mean with high probability under the
approximate posterior $q_\theta(W)$. Since \eqref{eq:c-gauss-vi} is Gaussian, $
  \tfrac{\lvert w - \mu \rvert^2}
        {\alpha \lvert \mu \rvert^2}
$ is $\chi^2_k$ distributed with shape $k=1$ ($\real$) or $2$ ($\cplx$), whence
\begin{equation} \label{eq:prob_relevant}
  \Pr\bigl(
    \lvert w - \mu \rvert \leq \delta \lvert \mu \rvert
  \bigr)
    = \Pr\biggl(
      \frac{\lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
        \leq \frac{\delta^2}{\alpha}
    \biggr)
    = \chi^2_k\biggl(\frac{\delta^2}{\alpha}\biggr)
  \,.
\end{equation}
% Figure~\ref{fig:hist__and__threshold__tradeoff} (bottom) shows the probability of a $\real$
% (or $\cplx$)  parameter being non-zero for various $\delta\in(0, \tfrac12)$ as a function
% of $\log \alpha$.
For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
$-2.5$ yield a relatively high chance of a non-zero parameter. Given that $q_\theta$
is merely an approximation, we opt for a somewhat higher $\log \alpha$ threshold, and
pick $\tau \in [-\tfrac12, \tfrac32]$, which is lower than $\tau = 3$, recommended by
\citet{molchanov_variational_2017}.

@@

% perfromance metrics
We use accuracy as the performance metric for multi-class image classification on MNIST-like
and CIFAR10 datasets. Similarly to \citet{trabelsi_deep_2017} the performance in MusicNet
experiments is measured with (pooled) average precision: predicted scores and target binary
labels for each output are pooled, and average precision is computed based on the precision-recall
curve as if the task was single-output.

The test performance is reported befire the beginning and after termination of the ``fine-tune''
stage. Additional rationale behind this decision is the extra fine tuning, which trains the
compressed model.

% write a note on the incompressible parameters (bias, batch norm etc.)
The compression rate is computed based on the number of floating point values needed
to specify the model and equals $
  \frac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
$, where $n_\mathtt{zer}$ is the number of explicit zeros after sparsification, $n_\mathtt{par}$
is the total number of floats. Thus each parameter is counted once in a $\real$-valued
network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
has incompressible parameters, such as layer biases, and shifts and scalings from $\real$-
and $\cplx$-batch normalization layers, if present.

@@

We conduct a moderately sized numerical experiment on MNIST and similar $28\times 28$
greyscale image datasets to study the compression-performance trade-off of the proposed
$\cplx$-variational dropout on simple architectures. We compare with the $\real$-valued
networks against their $\cplx$-valued counterparts with approximately half as many
parameters, as suggested by \citet{monning_evaluation_2018}.

@@

% model architectures
We study the following $\real$/$\cplx$ networks:
\begin{itemize}
  \item \textit{SimpleConvModel} (SCM): $2d$ convnet with Average pooling ($2\times 2$)
  with layers $c(n_1, 5, 1) \to c(n_2, 5, 1) \to d(n_3) \to d(n_\mathtt{out})$
  \item \textit{TwoLayerDenseModel} (TLDM): wide shallow network with structure
  $d(n_1) \to d(n_\mathtt{out})$
\end{itemize}
where $c(n, k, s)$ denotes a convolution with $n$ output channels, kernel width $k$ and
stride $s$, and $d(n)$ is a dense layer with $n$ outputs. The values of $n_\cdot$ depend
on the input features and are summarized in table~\ref{tbl:mnist-like-model-spec}.
\begin{table}[hb]
  \centering
  \caption{Architecture parameters for models studied on MNIST-like datasets.}
  \label{tbl:mnist-like-model-spec}
  \begin{tabular}{lrr}
    \toprule
    $(n_1, n_2, n_3)$  & $\real$-\textit{SCM} & $\cplx$-\textit{SCM} \\
    \midrule
    (\texttt{raw}) & $20, 50, 500$ & $10, 25, 250$ \\
    (\texttt{fft}) & $40, 100, 1000$ & $20, 50, 500$ \\
    \bottomrule
  \end{tabular}
  \begin{tabular}{lrr}
    \toprule
    $(n_1)$  & $\real$-\textit{TLDM} & $\cplx$-\textit{TLDM} \\
    \midrule
    (\texttt{raw}) & $4096$ & $2048$ \\
    (\texttt{fft}) & $8192$ & $4096$ \\
    \bottomrule
  \end{tabular}
\end{table}

@@

% discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
% hinting at overfitting/regularization effects of masking and sparsification

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
    (top) and \textit{SimpleConvModel} (bottom) for methods in sections~\ref{ssub:variational_dropout}
    and~\ref{ssub:empirical_bayes}.
  }
  \label{fig:mnist-like__trade-off}
\end{figure}

% which is better ARD or VD
It is worth pointing out that the prior used in ARD models offers slightly more favourable
compression-accuracy values, matching the established perception that log-uniform prior
is \todo{too harsh for sparsification tasks} \citep{kharitonov_variational_2018}.

@@

@@

% mention the same experimental setup as in MNIST
Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart, fit
on the full training split of $50k$ colour $32\times32$ images, and use only raw image
input features (\texttt{raw}).

% describe the VGG16 model and its cplx-valued modification
The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers
replaced by their $\cplx$-valued versions. To maintain comparability, we half the filter
sizes of $\cplx$ model.

@@

% compare compressed cplx-vgg against real-vgg
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__cifar10__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__cifar10__threshold/cifar10__threshold.pdf}
  \end{subfigure}
  \caption{%
    Pre ``fine-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
  }
  \label{fig:figure__cifar10__trade-off}
\end{figure}

% draw some conclusions

@@

\subsection{MusciNet} % (fold)
\label{sub:muscinet}

@@

We use training from sec.~\ref{sub:fitting_and_compression} with epochs lasting for $12$,
$32$ and $50$ epochs, respectively. Early stopping is used only during the ``fine-tune''
stage. Preliminary experiments with the model without sparsification have shown that early
stopping almost always terminated the training process within the first $10-20$ epochs,
and that the validation performance peaked at about $10-15$ epochs, much sooner than $200$
epoch, used by \citet{trabelsi_deep_2017}. Besides staged training and shorter ``dense''
stage, other important deviations from their setup include:
\begin{itemize}
  \item shifting lower frequencies to the centre of the window to maintain locality after
  applying FFT (much like in sec.~\ref{sub:mnist_like_datasets})
  \item clipping $\ell_2$ norm of parameters' gradients to $0.05$
  \item faster learning rate reduction schedule (sec.~\ref{sub:fitting_and_compression})
\end{itemize}
Each full three-stage experiment is replicated five times to take random effects into account,
e.g. random network initialization prior to ``dense'' stage, randomization of batches within
each epoch during SGD, and stochasticity of Bayesian forward pass at ``sparsify'' stage.

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__trade-off/legacy__musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
    uncompressed model.
    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{blue} VD}
    (\ref{ssub:variational_dropout}) and \textbf{\color{orange} ARD} (\ref{ssub:empirical_bayes});
    \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet__trade-off}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=1.\linewidth]{../notebooks/assets/grad_log.pdf}
  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed in
  \citet{molchanov_variational_2017}, MC estimate of \eqref{eq:improper-kl-div-real},
  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
  \label{fig:molchanov-derivative-replica}
\end{figure}

>>>>

% common experiment settings
Every experiment is replicated several times to take random effects into account, e.g.
random network initialization prior to training, randomly ordered batches during SGD.
Unless specified otherwise, every experiment uses global gradient clipping within an
$\ell_2$-norm ball of radius $0.5$, runs SGD with ADAM optimizer with the base learning
rate of $10^{-3}$. We note that since our experiments are on classification tasks,
$\cplx$-valued networks ultimately have to output a real-valued logit score. Following
\citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class scores are taken
as the real part of the $\cplx$ output.

\subsection{Stagewise fitting and compression} % (fold)
\label{sub:fitting_and_compression}

The goal of this section to study the compression-performance trade-off of the proposed Bayesian
sparsification methods for $\cplx$-valued networks. To this end we trained each network in
three successive stages in every experiment: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
Model parameters and the optimizer are copied between stages, except before the final stage
optimizer's internal state is reset.

At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
non-Bayesian architecture and using only the likelihood term from \eqref{eq:elbo} without
variational dropout.
%
During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes}) or its $\real$
counterpart. To be able to study the attainable sparsity levels we inject a coefficient $
  C \in (0, 1]
$ at the KL divergence term in \eqref{eq:elbo}:
\begin{equation}  \label{eq:elbo_with_coef}
    - \frac{C}N KL(q_{\theta} \| \pi_{\lambda})
    + \frac1{M} \sum_{i=1}^M
        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
    \,. \tag{\ref{eq:elbo}'}
\end{equation}
Higher $C$ yields increasingly more sparse layers upon termination of this stage.

The \textit{``fine-tune''} stage begins with computing the sparsity masks from the fitted
approximation $q_\theta(W)$ and proceeds to train the non-zero parameters similarly to
the ``dense'' stage, i.e. with non-Bayesian layers and fixed sparsity masks.
%
\todo{reword}
We observe dual effect of ``fine-tune'' stage: it improves performance of highly compressed
models since they are more regularized (by poking holes) and thus serves as further fitting.
At the same time, undercompressed models, behave as if they were over parameterized
and the fine tune stage overfits.

% on compresssion
Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
the variational approximation factorizes into univariate distributions, whether a $\cplx$
or $\real$ parameter is zero or not is determined from individual relevance scores $
  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff}
displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset
in sec.~\ref{sub:mnist_like_datasets}. This shape appears to be typical in every experiment
conducted in this study: there always is a single mode within the moderately negative
range, and one or two modes to the right of zero. The relative mass of each mode changes
with $C$ and the higher the coefficient is, the more mass is shifted to the right. In every
experiment the trough between the peaks of the negative mode and the first positive one
is around zero.
%
The bottom plot on figure~\ref{fig:hist__and__threshold__tradeoff} is constructed without
running the ``fine-tune'' stage for $C=\tfrac1{2000}$, $\tfrac1{20}$, and $\frac1{200}$.
The latter setting yields one of the better performing models on the validation split in
sec.~\ref{sub:musicnet}. We can observe that by choosing $\tau > 0$ we end up in the
saturation region of the performance and gain only marginal improvement, while losing
in compression. Relative position compression curves shows that $C$ has much more substantial
impact on the target sparsity and performance, than the choice of $\tau$.

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/log-alpha__sum__fashion-mnist__20200131-205926.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/figure__musicnet__threshold.pdf}
  \end{subfigure}
  \caption{%
    (\textit{top}) Smoothed density of $\log\alpha$ for some convolutional and dense layer
    from a model in sec.~\ref{sub:mnist_like_datasets};
    (\textit{bottom}) Test split performance and compression rate for $\cplx$-valued net
    by \citet{trabelsi_deep_2017} on MusicNet.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

% on chosing the threshold
The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
are within $\delta$ relative tolerance of their mean with high probability under the
approximate posterior $q_\theta(W)$. Since \eqref{eq:c-gauss-vi} is Gaussian, $
  \tfrac{\lvert w - \mu \rvert^2}
        {\alpha \lvert \mu \rvert^2}
$ is $\chi^2_k$ distributed with shape $k=1$ ($\real$) or $2$ ($\cplx$), whence
\begin{equation} \label{eq:prob_relevant}
  \Pr\bigl(
    \lvert w - \mu \rvert \leq \delta \lvert \mu \rvert
  \bigr)
    = \Pr\biggl(
      \frac{\lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
        \leq \frac{\delta^2}{\alpha}
    \biggr)
    = \chi^2_k\biggl(\frac{\delta^2}{\alpha}\biggr)
  \,.
\end{equation}
For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
$-2.5$ yield a relatively high chance of a non-zero parameter. Setting $\tau = 3$
\citep{molchanov_variational_2017,kingma_variational_2015} is, in our opinion, detrimental
since it retains parameters $W \sim q_\theta$, standard deviation of which significantly
exceeds the magnitude of $\mu$, which is typically used as a stand-in for $W$ when the
network is run in inference mode. Given that $q_\theta$ is merely an approximation,
we pick $\tau = -\tfrac12$ as the sparsification threshold for $\log \alpha$ in our
experiments.

@@

% perfromance metrics
We use accuracy as the performance metric for multi-class image classification on MNIST-like
and CIFAR10 datasets. Similarly to \citet{trabelsi_deep_2017} the performance in MusicNet
experiments is measured with (pooled) average precision: predicted scores and target binary
labels for each output are pooled, and average precision is computed based on the precision-recall
curve as if the task was single-output. The evaluation is done after ``dense'' stage, before
the beginning and upon termination of the ``fine-tune'' stage.

% write a note on the incompressible parameters (bias, batch norm etc.)
The compression rate is computed based on the number of floating point values needed
to specify the model and equals $
  \frac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
$, where $n_\mathtt{zer}$ is the number of explicit zeros after sparsification, $n_\mathtt{par}$
is the total number of floats. Thus each parameter is counted once in a $\real$-valued
network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
has incompressible parameters, such as layer biases, shift and scaling from $\real$-and
$\cplx$-batch normalization layers, if present.

@@

We conduct a moderately sized numerical experiment on MNIST and similar $28\times 28$
greyscale image datasets to study the compression-performance trade-off of the proposed
$\cplx$-variational dropout on simple architectures.

@@

% model architectures
% discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
 the following :
To compactly describe the $\real$/$\cplx$ networks we study in this experiment we use
the following notation: $c(n, k, s)$ is a convolution with $n$ output channels, kernel
width $k$ and stride $s$, and $d(n)$ is a dense layer with $n$ outputs. The values of
$n_\cdot$ depend on the input features and are summarized in table~\ref{tbl:mnist-like-model-spec}.
\begin{itemize}
  \item \textit{SimpleConvModel} (SCM): $2d$ convnet with Average pooling ($2\times 2$)
  with layers $c(n_1, 5, 1) \to c(n_2, 5, 1) \to d(n_3) \to d(n_\mathtt{out})$
  \item \textit{TwoLayerDenseModel} (TLDM): wide shallow network with structure
  $d(n_1) \to d(n_\mathtt{out})$
\end{itemize}

\begin{table}[hb]
  \centering
  \caption{Architecture parameters for models studied on MNIST-like datasets.}
  \label{tbl:mnist-like-model-spec}
  \begin{tabular}{lrr}
    \toprule
    $(n_1, n_2, n_3)$  & $\real$-\textit{SCM} & $\cplx$-\textit{SCM} \\
    \midrule
    (\texttt{raw}) & $20,  50,  500$ & $10, 25, 250$ \\
    (\texttt{fft}) & $40, 100, 1000$ & $20, 50, 500$ \\
    \bottomrule
  \end{tabular}
  \begin{tabular}{lrr}
    \toprule
    $(n_1)$  & $\real$-\textit{TLDM} & $\cplx$-\textit{TLDM} \\
    \midrule
    (\texttt{raw}) & $4096$ & $2048$ \\
    (\texttt{fft}) & $8192$ & $4096$ \\
    \bottomrule
  \end{tabular}
\end{table}

% first experiment: 40-75-40 with fast scheduler
First we try to compare the $\real$-valued networks against their $\cplx$-valued counterparts
with approximately half as many parameters, as suggested by \citet{monning_evaluation_2018}.
In this experiment, ``dense'', ``sparsify'' and ``fine-tune'' stages last for $40$, $75$
and $40$ epochs, respectively. The base learning rate is scaled after $5$, $10$, and $20$
epochs by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.

@@

% which is better ARD or VD
It is worth pointing out that the prior used in ARD models offers slightly more favourable
compression-accuracy values, matching the established perception that log-uniform prior
is too harsh for sparsification tasks \citep{kharitonov_variational_2018}.

Nevertheless, it is clear form the results depicted in \ref{where}, that VD and ARD
methods yield very similar compression-performance frontiers.

% second experiment: use scheduler Trabelsi et al. (2018) and show them plotz!
In the second experiment we use a much slower learning rate scheduler and study only the 
VD method.

% hinting at overfitting/regularization effects of masking and sparsification

@@

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
    (top) and \textit{SimpleConvModel} (bottom) for methods in sections~\ref{ssub:variational_dropout}
    and~\ref{ssub:empirical_bayes}.
  }
  \label{fig:mnist-like__trade-off}
\end{figure}

@@

% mention the same experimental setup as in MNIST
Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart. Each
network is trained stagewise for $20$, $40$, and $20$ epochs on the full training split
of $50k$ colour $32\times32$ images. We use only raw colour features (\texttt{raw}), since
the results of the experiments on MNIST left us sceptical about the utility of the Fourier
features for image recognition. We use fast learning rate scheduler from sec.~\ref{sub:mnist_like_datasets}.

@@

% describe the VGG16 model and its cplx-valued modification
The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers
replaced by their $\cplx$-valued versions. To maintain comparability, we halve the
filter sizes of $\cplx$ model \citep{monning_evaluation_2018}.

% compare compressed cplx-vgg against real-vgg
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=\linewidth]{../assets/figure__cifar10__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=\linewidth]{../assets/figure__cifar10__threshold/cifar10__threshold.pdf}
  \end{subfigure}
  \caption{%
    Pre ``fine-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
  }
  \label{fig:figure__cifar10__trade-off}
\end{figure}

% draw some conclusions
The halved $\cplx$ network significantly underperforms in comparison with its $\real$ counterpart

@@

\subsection{MusciNet} % (fold)
\label{sub:musicnet}

@@

We use training from sec.~\ref{sub:fitting_and_compression} with epochs lasting for $12$,
$32$ and $50$ epochs, respectively. Early stopping is used only during the ``fine-tune''
stage. Preliminary experiments with the model without sparsification have shown that early
stopping almost always terminated the training process within the first $10-20$ epochs,
and that the validation performance peaked at about $10-15$ epochs, much sooner than $200$
epoch, used by \citet{trabelsi_deep_2017}. Besides stagewise training and shorter ``dense''
stage, other important deviations from their setup include:
\begin{itemize}
  \item shifting lower frequencies to the centre of the window to maintain locality after
  applying FFT (much like in sec.~\ref{sub:mnist_like_datasets})
  \item clipping $\ell_2$ norm of parameters' gradients to $0.05$
  \item faster learning rate reduction schedule (sec.~\ref{sub:fitting_and_compression})
\end{itemize}
Each full three-stage experiment is replicated five times to take random effects into account,
e.g. random network initialization prior to ``dense'' stage, randomization of batches within
each epoch during SGD, and stochasticity of Bayesian forward pass at ``sparsify'' stage.

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
    uncompressed model.
    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{blue} VD}
    (\ref{ssub:variational_dropout}) and \textbf{\color{orange} ARD} (\ref{ssub:empirical_bayes});
    \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet__trade-off}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\linewidth]{../notebooks/assets/grad_log.pdf}
  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed in
  \citet{molchanov_variational_2017}, MC estimate of \eqref{eq:improper-kl-div-real},
  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
  \label{fig:molchanov-derivative-replica}
\end{figure}
